Working Principles of Proof Assistants and Formalization of some proofs in Agda

### 2025-08-05 Mainpaper/paper.tex
small changes tried some euclid codes
workarounds

>>>>

\begin{itemize}
    \item In 5.1, we define natural numbers and their equality (When can we say two numbers are equal) from scratch. Defining the basic objects in every proof we write is tedious, therefore we use Agda's Standard Library and use pre defined and some pre-proven results to work further.
    \item In 5.3, the forward direction was do able with constructive principles. But for the other way, we used law of excluded middle by importing Dec from Relation.Nullary.
    \item 
\end{itemize}
